---
title: "The Artist"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<div class = 'row'>
  <div class = 'col-sm-6'>

Daryl Moore has spent his life in Southern Ontario. He was born in Toronto in 1967, and moved around a lot as a child. His diverse experiences fostered a love of the both the arts and the outdoors. Daryl spent his teenage years beginning his life-long career in the trades, and in his twenties, met and married the love of his life, Monika Halova. As a successful actress, Monika found great pleasure in the arts and, after seeing Daryl's skills displayed through a hobby art kit in 1999, nurtured Daryl's painting talents with love and support. After twenty years of marriage and the raising of four sons, Monika tragically passed away in 2010. Since then, Daryl has taken to painting more and more, finding ways to express himself through putting paint to canvas.

Daryl describes his work as "Marvel Comics meets Bob Ross" - a melding of his two greatest artistic inspirations. While he generally paints his own impression of photographs using bold colouring with a mix of depth and focus, Daryl has also worked from studio sittings, still life, and custom request commissions. Daryl generally works in acryllic on canvas, but is also experienced in painting on wood surfaces. 

Recently, Daryl has received local praise from his community in Mount Albert, ON for displaying his painting in his home's front window facing Main Street. He enjoys a deep satisfaction watching the passers by stare up at his work in astonishment, wonder, and curiosity. As Daryl says, "I just want my art to make people happy. Putting a new painting out there for people to see, especially during COVID, has been my way of reaching out and showing my heart in these trying times."
  </div>
  
  <div class = 'col-sm-6'>
  <img src = "https://zacharymilosmoore.github.io/mooremanordesigns/photos/DarylPainting.jpg" >
  </div>
</div>
<div class="header">

Last Updated: 
```{r,results="asis",echo=F} 

cat(format(Sys.time(),"%c"))
```
[GitHub Source](https://github.com/zacharymilosmoore/mooremanordesigns)

</div>